The problem and promise of scale in multilayer animal social networks

### 2020-02-10 paper/manuscript.Rmd
title
conclusion - 1st draft

---
title: The problem and promise of scale in animal social multilayer networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
   # github_document
  bookdown::pdf_document2:
     number_sections: false
  #bookdown::word_document2:
   # reference_docx: template.docx
bibliography: ../references/knitcite.bib
---

@@

Our study is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (*Rangifer tarandus*) in
Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in the social, spatial, and
temporal improve predictions associated with biological differences in seasonal
resource availability and social association? We conclude with perspectives for
further development and application of scale in multilayer networks with respect
to phenotypes and individual fitness [@Webber_2018], movement ecology and
collective movement [@Jolles_2019], and habitat selection and space use. <!--
TODO: (REF)--> <!-- TODO: Webber reference should be 2018, but defaulting to
2017-->

@@

Silk et al. (2018) summarized some key multilayer questions in animal behaviour
research. While these questions are important for linking animal behaviour and
multilayer networks, we present an additional set of questions posed through the
lense of spatial ecology and relevant to the promise and problem of scale in
mutlilayer networks:

1. How do social phenotypes vary across social scales and differentially influence fitness? Are
some temporal or social scales better predictors for different fitness metrics?

2. Why do individuals associate more strongly with certain conspecifics in some
habitats? What, if any, is the role of movement in the context of habitat
networks?

3. How, and why, does the spatial scale of perception influence, e.g. auditory,
visual, or chemotaxis, influence the  social environment? What is
the role of memory, and by extension social and spatial cognition, as animals
navigate their environment and make decisions about where to move next?

>>>>

---
title: The problem and promise of scale in multilayer animal social networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
   # github_document
  bookdown::pdf_document2:
     number_sections: false
  #bookdown::word_document2:
   # reference_docx: template.docx
bibliography: ../references/knitcite.bib
---

@@

Our study is motivated by behavioural, landscape, and spatial ecology to build a
conceptual and analytical framework for scale-dependent multilayer networks and
we apply this framework to a case study of caribou (*Rangifer tarandus*) in
Newfoundland, Canada [@Peignier_2019]. We use this case study to address two
principal questions associated with scale-dependent multilayer networks. First,
to what degree does the social scale of relationships, spatial scale of
landscapes, and temporal scale of analysis influence our ability to interpret
complex social systems? Second, can variation in the social, spatial, and
temporal scale improve predictions associated with biological differences in seasonal
resource availability and social association? We conclude with perspectives for
further development and application of scale in multilayer networks with respect
to phenotypes and individual fitness [@Webber_2018], movement ecology and
collective movement [@Jolles_2019], and habitat selection and space use. <!--
TODO: (REF)--> <!-- TODO: Webber reference should be 2018, but defaulting to
2017-->

@@

With our caribou case stuyd, we show that (1) multilayer social networks can be,
but are not always, scale dependent and (2) that the use of multilayer networks
could be useful for identifying habitat or season-specific social processes. Our
analyses of social, spatial, and temporal scales in multilayer network framework
highlight potential to identify scales at which variation in properties of
layers within a multilayer network show the most variability. Our analysis of
caribou multilayer networks incorporated high resolution GPS telemetry data and
spatial landcover data, thus allowing us ground our broader discussion of
multilayer networks in the context of observed animal social networks.
<!--QW: I am not very happy with this paragraph, but it's a start -->

Multilayer networks remain a nascent tool in animal behavioural ecology. We
demonstrate novel analyses that vary social, spatial, and temporal scale within
a multilayer framework and we discuss the potential integration of individual
phenotypes and fitness, collective movememtn, and habitat selection for future
analyses considering spatial ecology  using multilayer networks. Silk et al.
(2018) summarized some key multilayer questions in animal behaviour research.
While these questions are important for linking animal behaviour and multilayer
networks, we summarize our perspectives on the future of multilayer networks
with an additional set of questions posed through the lense of spatial ecology
that are relevant to the promise and problem of scale in mutlilayer networks:

1. How do social phenotypes vary across social scales and differentially
influence fitness? Are some temporal or social scales better predictors for
different fitness metrics?
2. Why do individuals associate more strongly with certain conspecifics in some
habitats? What, if any, is the role of movement in the context of habitat
networks?
3. How, and why, does the spatial scale of perception influence, e.g. auditory,
visual, or chemotaxis, influence the  social environment? What is the role of
memory, and by extension social and spatial cognition, as animals navigate their
environment and make decisions about where to move next?
